\textbf{ Accurate spectrophotometric estimates of luminosity and distance\\ for luminous red-giant stars }

### 2018-07-27 paper/sp.tex
author order; tweaks

@@

As we operate these spectroscopic surveys,
the \gaia\ Mission has been revolutionizing our view of the disk.
It delivers good proper motions everywhere,
and extremely valuable parallax information
locally.
However, it does not deliver precise geometric parallaxes over a large fraction of
the disk, and certainly not in the dusty and crowded regions.
For these reasons, the value of \gaia\ in these infrared sky projects is not
to deliver distance information directly, but rather to calibrate stellar models,
which then deliver distance information through relationships between stellar
luminosities and spectral characteristics.

>>>>

\author[0000-0003-2866-9403]{David W. Hogg}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University}
\affiliation{Center for Data Science, New York University}
\affiliation{Max-Planck-Institut f\"ur Astronomie}
\affiliation{Flatiron Institute}

@@

As we operate these spectroscopic surveys,
the \gaia\ Mission has been revolutionizing our view of the disk.
It delivers good proper motions everywhere,
and extremely valuable parallax information
locally.
However, it does not deliver precise geometric parallaxes over a large fraction of
the disk, and certainly not in the dusty and crowded regions.
For these reasons, the value of \gaia\ in these infrared spectroscopy projects is not
to deliver distance information directly, but rather to calibrate stellar models,
which then deliver distance information through relationships between stellar
luminosities and spectral characteristics.
